---
title: "Synchrony_12.29.20"
output: html_document
---
Next steps: 
(1) Get infant sex --> Birth chart data (figure out who is missing, update with birthcharts, and contact Van with birth chart, and Shreya/Monica/Vanessa look at videos---ask Alyssa) (Association between infant sex and maternal testosterone)--> I emailed Darby about the file that didn't work; she is getting me a new one
(2) How to select cases for demographics (include people with missing data points---how to compare them--t-test even if uneven sizes to say there aren't big differences; see if the fifteen if first t mps onto average t)
(3) Outliers for hormone data ---include the people with one sample and try analyses with and without 

## Preparationn
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r dataFrames, echo=TRUE, eval=TRUE}

```

```{r Load packages, message=FALSE}
# Add additional packages you need
# To install a package, run the following ONCE (and only once on your computer)
# install.packages("psych")  
# install.packages ("ggpubr")
# install.packages("Publish")
# install.packages("ggubr")
# install.packages("corrplot")
# install.packages("RColorBrewer")
# install.packages("ggpubr")
# install.packages("lme4")
# install.packages("lmerTest")
# install.packages("multilevelTools")
# install.packages("pastecs")
# install.packages("qwraps2")
# install.packages(apaTables)
# install.packages(apa.d.table)
# install.packages(apa.descriptive)
# install.packages(apa.cor.table)
# install.packages(Gmisc)
# install.packages('ltm')

library(ltm)
library(qwraps2)
library(multilevelTools)
library(lme4)
library(lmerTest)
library(ggpubr)
library(Publish) 
library(here)  # makes reading data more consistent
library(haven)  # for importing SPSS/SAS/Stata data
library(brms)  # for Bayesian multilevel analysis
library(lattice)  # for dotplot (working with lme4)
library(sjPlot)  # for plotting effects
library(broom.mixed)  # for summarizing results
library(interactions)  # for plotting interactions
library(modelsummary)  # for making tables
library(psych)
library(ggpubr)
library(lmerTest)
library(corrplot)
library(RColorBrewer)
library(ggpubr)
library(pastecs)
library(apaTables)
library(tidyr)
library(dplyr)
library(tidyverse)  # for data manipulation and plotting
library(haven)  # for importing SPSS/SAS/Stata data
library(brms)  # for Bayesian multilevel analysis
library(lattice)  # for dotplot (working with lme4)
library(interactions)  # for plotting interaction

# Add the following so that the LOO will be included in the msummary table
msummary_mixed <- function(models, coef_map = NULL, add_rows = NULL, ...) {
  if (is.null(coef_map)) {
    if (!"list" %in% class(models)) {
      models <- list(models)
    }
    for (model in models) {
      coef_map <- union(coef_map, tidy(model)$term)
    }
  }
  ranef_index <- grep("^(sd|cor)__", x = coef_map)
  coef_map <- c(coef_map[-ranef_index], coef_map[ranef_index])
  names(coef_map) <- coef_map
library(dplyr)
  rows <- data.frame(term = c("Fixed Effects", "Random Effects"))
  rows <- cbind(rows, rbind(rep("", length(models)), 
                            rep("", length(models))))
  length_fes <- length(coef_map) - length(ranef_index)
  attr(rows, 'position') <- c(1, (length_fes + 1) * 2)
  modelsummary::msummary(models, coef_map = coef_map, add_rows = rows, ...)
}
theme_set(theme_bw())  # Theme; just my personal preference
```
# When working with new SPSS folder, rename Test Variables in SPSS

1. Rename testosterone variables in SPSS...
Testo1pn.1.trunc--->Mompn1
Testo3pn.1.trunc--->Mompn2
Testo6pn.1.trunc--->Mompn3
Testo1pn.2.trunc--->Dadpn1
Testo3pn.2.trunc--->Dadpn2
Testo6pn.2.trunc--->Dadpn3
Testo1pp.1trunc--->Mompp1
Testo3pp.1trunc--->Mompp2
Testo6pp.1trunc--->Mompp3
Testo1pp.2.00--->Dadpp1
Testo3pp.2.00--->Dadpp2
Testo6pp.2.00--->Dadpp3

2. Make new variable by calculating the weeks pregnant by dividing dayspreg.1/7
dayspreg.1--->WeeksPregnant.1 (optional)


3. Make new variable by calculate average scores in SPSS...
MomTesto1
DadTesto1
MomTesto2
DadTesto2
monthspreg.1
weekspreg.1
bage6pp.months

4. Move these variables to the front...
CoupID
RelStat
pnAge_1.1
pnAge_1.2
Ethnicity.1
Ethnicity.2
Education.1
Education.2
Baby.sex
monthspreg.1
weekspreg.1
dayspreg.1
bage6pp.months
bage6pp
bage3pp.1
bage3pp.2
Mompn1
Mompn2
Mompn3
Dadpn1
Dadpn2
Dadpn3
Mompp1
Mompp2
Mompp3
Dadpp1
Dadpp2
Dadpp3
MomTesto1
DadTesto1
MomTesto2
DadTesto2
PARYCse.1
PARYCse.2
PARYCpa.1
PARYCpa.2
PARYCtot.1
PARYCtot.2
DAStotpp.1
DAStotpp.2
pnMaritalSat.1
pnMaritalSat.2
MAT1pp
MAT2pp
PBQ.1
PBQ.2

5.Save the dataset with "_extra" where the first 18 people have their one data point as their average

# Prenatal Equations

Level-1:
$$\text{Father_Prenatal_Testosterone}_{ij} = \beta_{0j} + \beta_{1j}Mother\_Prenatal\_Testosterone{ij} + \beta_{2j}Father\_Age{ij} + \beta_{3j}Mother\_Weeks\_Pregnant{ij} + e_{ij}$$   

Father_Prenatal_Testosterone_ij = refers to the score on the dependent variable for an individual observation at Level 1 (subscript i refers to individual case, subscript j refers to the couple).
Beta_0j = refers to the intercept of the dependent variable in couple j (Level 2).
Beta_1j_Mother_Prenatal_Testosterone_ij= refers to the slope for the relationship in couple j (Level 2) between the Level 1 predictor and the dependent variable.
Beta_2j_Father_Age_ij= refers to the slope for the relationship in couple j (Level 2) between the Level 1 predictor and the dependent variable.
Beta_3j_Mother_Weeks_Pregnant_ij= refers to the slope for the relationship in couple j (Level 2) between the Level 1 predictor and the dependent variable.
e_ij=  refers to the random errors of prediction for the Level 1 equation.  
 
 Level-2
$$\beta_{0j} = \gamma_{00} + \gamma_{01}Mother\_Prenatal\_Testosterone_j + u_{0j}$$   

Beta_0j = refers to the intercept of the dependent variable in couple j (Level 2).
gamma_00 = refers to the overall intercept. This is the grand mean of the scores on the dependent variable across all the couple when all the predictors are equal to 0.
gamma_01_Mother_Prenatal_Testosterone_j= refers to the overall regression coefficient, or the slope, between the dependent variable and the Level 2 predictor.
u_0j= refers to the random error component for the deviation of the intercept of a couple from the overall intercept.

$$\beta_{1j} = \gamma_{10} + u_{1j}$$  

Beta_1j = refers to the slope for the relationship in couple j (Level 2) between the Level 1 predictor and the dependent variable.
gamma_10 = refers to the overall regression coefficient, or the slope, between the dependent variable and the Level 1 predictor.
u_1j = refers to the error component for the slope (meaning the deviation of the group slopes from the overall slope).
 
# Postpartum Equations

$$\text{Father_Postpartum_Testosterone}_{ij} = \beta_{0j} + \beta_{1j}Mother\_Postpartum\_Testosterone{ij} + \beta_{2j}Father\_Age{ij} + \beta_{3j}Baby\_Age{ij} + e_{ij}$$    

Beta_0j = refers to the intercept of the dependent variable in couple j (Level 2).
Beta_1j_Mother_Postpartum_Testosterone_ij= refers to the slope for the relationship in couple j (Level 2) between the Level 1 predictor and the dependent variable.
Beta_2j_Father_Age_ij= refers to the slope for the relationship in couple j (Level 2) between the Level 1 predictor and the dependent variable.
Beta_3j_Baby_Age_ij= refers to the slope for the relationship in couple j (Level 2) between the Level 1 predictor and the dependent variable.
e_ij=  refers to the random errors of prediction for the Level 1 equation
 
 Level-2
$$\beta_{0j} = \gamma_{00} + \gamma_{01}Mother\_Postpatum\_Testosterone_j + u_{0j}$$     

Beta_0j = refers to the intercept of the dependent variable in group j (Level 2).
gamma_00 = refers to the overall intercept. This is the grand mean of the scores on the dependent variable across all the couple when all the predictors are equal to 0.
gamma_01_Mother_Postpartuml_Testosterone_j= refers to the overall regression coefficient, or the slope, between the dependent variable and the Level 2 predictor.
u_0j= refers to the random error component for the deviation of the intercept of a couple from the overall intercept.

$$\beta_{1j} = \gamma_{10} + u_{1j}$$   

Beta_1j = refers to the slope for the relationship in couple j (Level 2) between the Level 1 predictor and the dependent variable.
gamma_10 = refers to the overall regression coefficient, or the slope, between the dependent variable and the Level 1 predictor.
u_1j = refers to the error component for the slope (meaning the deviation of the group slopes from the overall slope).

# Data preparation
```{r Import Data}
library(foreign)
df_WIDE <- read.spss('/Users/sofiacardenas/Desktop/MLM(psyc575)/Final_Project/HATCH_12.10.2020.sav', use.value.label=TRUE, to.data.frame=TRUE)
df_WIDE
```

```{r Make dad prenatal and postpartum variable}
df_WIDE <- df_WIDE %>% 
    mutate(Dad_Change = DadTesto1 - DadTesto2)
```

```{r}
df_WIDE$Baby.sex <- factor(df_WIDE$Baby.sex)
```

```{r Convert Wide Data to Long Format}
# Using the new `tidyr::pivot_longer()` function
df_LONG <- df_WIDE %>% 
  pivot_longer(
    c(Mompn1:Mompn3, Dadpn1:Dadpn3, Mompp1:Mompp3, Dadpp1:Dadpp3), # variables that are repeated measures
    # Convert 8 columns to 3: 2 columns each for anti/read (.value), and 
    # one column for time
    names_to = c(".value", "Testo_Measurement"),
    # Extract the names "anti"/"read" from the names of the variables for the 
    # value columns, and then the number to the "time" column
    names_pattern = "(Mompn|Dadpn|Mompp|Dadpp)([1-3])", 
    # Convert the "time" column to integers
    names_transform = list(time = as.integer)
    )
df_LONG %>% 
  select(CoupID, Testo_Measurement, Mompn, Dadpn, Mompp, Dadpp, everything())
``` 

```{r First long format}
df_LONG <- df_LONG %>% 
  select(CoupID, Mompn, Testo_Measurement, everything())
```

# Making unconditional models for all prenatal variables

```{r message=FALSE, warning=FALSE}
m0_Model_daddy <- brm(Dadpn ~ (1 | CoupID), data = df_LONG, 
               seed = 2152)
echo=FALSE
```

```{r}
m0_Model_daddy
```

# Using unconditional models to assess prenatal intra-class correlation and decompose variance
```{r}
# Warning: Rows containing NAs were excluded from the model.
# Daddy (expectant dad-testosterone)
post_daddy <- posterior_samples(m0_Model_daddy, pars = c("sd", "sigma"))

# Posterior of ICC: tau_0^2 / (tau_0^2 + sigma^2)
icc_samples_daddy <- post_daddy$sd_CoupID__Intercept^2 / 
  (post_daddy$sd_CoupID__Intercept^2 + post_daddy$sigma^2)

# Print ICCs
c(daddy = mean(icc_samples_daddy))
```

```{r Prenatal MLM model }
Bayesian_Synchrony_Prenatal_Larger <- brm(Dadpn ~ pnAge_1.2 + monthspreg.1 + Mompn + (Mompn | CoupID),
               seed = 2153,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

```{r Results Prenatals Synchrony Model}
Bayesian_Synchrony_Prenatal_Larger
```

```{r Figure of prenatal mothers testerone predicting fathers prenatal testosterone}

augment(Bayesian_Synchrony_Prenatal_Larger) %>% 
  mutate(Mompn = Mompn) %>% 
  ggplot(aes(x = Mompn, y = Dadpn, color = factor(CoupID))) +
  # Add points
  geom_point(size = 0.5, alpha = 0.2) + 
  # Add within-cluster lines
  geom_smooth(aes(y = .fitted), 
              method = "lm", se = FALSE, size = 0.5) + 
  # Add group means
  stat_summary(aes(x = Mompn, y = .fitted, 
                   fill = factor(CoupID)), 
               color = "red",  # add border
               fun = mean, 
               geom = "point",
               shape = 24,
               # use triangles
               size = 2.5) + 
  # Add between coefficient
  geom_smooth(aes(x = Mompn, y = .fitted), 
              method = "lm", se = TRUE, 
              color = "black") + 
  labs(y = "Dadpn") + 
  # Suppress legend
  guides(color = FALSE, fill = FALSE)
```

# Making unconditional models for all postpartum variables

```{r message=FALSE, warning=FALSE}
m0_Model_daddy_2 <- brm(Dadpp ~ (1 | CoupID), data = df_LONG, 
               seed = 2152)
echo=FALSE
```

```{r}
m0_Model_daddy_2
```

# Using unconditional models to assess prenatal intra-class correlation and decompose variance
```{r}
# Warning: Rows containing NAs were excluded from the model.
# Daddy (expectant dad-testosterone)
post_daddy_2 <- posterior_samples(m0_Model_daddy_2, pars = c("sd", "sigma"))

# Posterior of ICC: tau_0^2 / (tau_0^2 + sigma^2)
icc_samples_daddy_2 <- post_daddy_2$sd_CoupID__Intercept^2 / 
  (post_daddy_2$sd_CoupID__Intercept^2 + post_daddy_2$sigma^2)

# Print ICCs
c(daddy_2 = mean(icc_samples_daddy_2))

```

# Postpartum MLM model 
```{r}
Bayesian_Synchrony_Postpartum_Larger <- brm(Dadpp ~ pnAge_1.2 + bage6pp.months + Mompp + (Mompp | CoupID),
               seed = 2153,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 6000, data = df_LONG)

```

```{r}
Bayesian_Synchrony_Postpartum_Larger
```

```{r Figure 2 }
augment(Bayesian_Synchrony_Postpartum_Larger) %>% 
  mutate(Mompn = Mompp) %>% 
  ggplot(aes(x = Mompp, y = Dadpp, color = factor(CoupID))) +
  # Add points
  geom_point(size = 0.5, alpha = 0.2) + 
  # Add within-cluster lines
  geom_smooth(aes(y = .fitted), 
              method = "lm", se = FALSE, size = 0.5) + 
  # Add group means
  stat_summary(aes(x = Mompp, y = .fitted, 
                   fill = factor(CoupID)), 
               color = "red",  # add border
               fun = mean, 
               geom = "point",
               shape = 24,
               # use triangles
               size = 2.5) + 
  # Add between coefficient
  geom_smooth(aes(x = Mompp, y = .fitted), 
              method = "lm", se = TRUE, 
              color = "black") + 
  labs(y = "Dadpp") + 
  # Suppress legend
  guides(color = FALSE, fill = FALSE)
```

```{r Create new variable Prenatal Synchrony}
beta <-ranef(Bayesian_Synchrony_Prenatal_Larger)
beta
```

```{r}
beta_beta <- beta$CoupID[ , , "Mompn"]
beta_beta
```

```{r}
synchrony <- beta_beta[ ,"Estimate"]
synchrony
```

```{r}
synchrony <- as.data.frame(synchrony)
synchrony
```

```{r}
df_WIDE <- df_WIDE %>%
  mutate(CoupID=as.character(CoupID))
```

```{r}
synchrony <- rownames_to_column(synchrony, "CoupID")
synchrony
```

```{r Add Prenataal Synchrony to the dataset}
finaldt <- left_join(df_WIDE, synchrony)
finaldt
```

# Postpartum Synchrony 
```{r}
beta_2 <-ranef(Bayesian_Synchrony_Postpartum_Larger)
beta_2
```

```{r}
beta_beta_2 <- beta_2$CoupID[ , , "Mompp"]
beta_beta_2
```

```{r}
synchrony_2 <- beta_beta_2[ ,"Estimate"]
synchrony_2
```

```{r}
synchrony_2<- as.data.frame(synchrony_2)
synchrony_2
```

```{r}
df_WIDE <- df_WIDE %>%
  mutate(CoupID=as.character(CoupID))
```

```{r}
synchrony_2 <- rownames_to_column(synchrony_2, "CoupID")
synchrony_2
```

```{r}
finaldt_2 <- left_join(df_WIDE, synchrony_2)
finaldt_2
```

```{r}
finaldt_2 %>% 
  select(CoupID, synchrony_2, Dad_Change, everything())
finaldt_2
```

# Prenatal Synchrony and Testosteone Change Prenatal to Postpartum

```{r Looking at Dad Change Testosterone}
finaldt$Dad_Change
summary(finaldt$Dad_Change)
```

```{r Looking at Couple Synchrony}
finaldt$synchrony
summary(finaldt$synchrony)
```

# Put synchrony into one set

```{r Prenatal_synchrony}
Prenatal_synchrony <- finaldt$synchrony
```

```{r Postpartum synchrony}
Postpartum_synchrony <- finaldt_2$synchrony_2
```

```{r Put Prenatal and Postpartum Synchrony into one set}
finaldt_3 <- left_join(finaldt_2, synchrony)
finaldt_3
```

```{r}
finaldt_3 %>% 
  select(CoupID, synchrony, synchrony_2, everything())
```

```{r}
finaldt_3 %>% 
  select(CoupID, synchrony, synchrony_2, Dad_Change, everything())
```

```{r}
finaldt_4 <- subset(finaldt_3, synchrony != "NA" | synchrony_2 != "NA")
finaldt_4

```

```{r}
finaldt_4 %>% 
  select(CoupID, synchrony, synchrony_2, Dad_Change, everything())
```

# Prenatal Synchrony & Fathers' Testosterone Changes
```{r Prenatal Synchrony and Testosteone Change Prenatal to Postpartum}
linearMod_CHANGE <- lm(Dad_Change ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearMod_CHANGE)
summary.lm(linearMod_CHANGE)
```

```{r Scatterplot of Prenatal Synchrony and Dad Change}
ggscatter(finaldt_4, x = "synchrony", y = "Dad_Change", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Fathers' Testosterone Change from Prenatal to Postpartum")
```

# Synchrony & Attachment 
```{r Prenatal Synchrony and Maternal Attachment}
linearPrenatalSynchrony_MaternalAttachment <- lm(PBQ.1 ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_MaternalAttachment)
summary(linearPrenatalSynchrony_MaternalAttachment)
```

```{r Graph Prenatal Synchrony and Maternal Attachment}
ggscatter(finaldt_4, x = "synchrony", y = "PBQ.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Mother Postpartum Parental Bonding")
```

```{r Prenatal Synchrony and Paternal Attachment}
linearPrenatalSynchrony_PaternalAttachment <- lm(PBQ.2 ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_PaternalAttachment)
summary(linearPrenatalSynchrony_PaternalAttachment)
```

```{r Results Prenatal Synchrony and Paternal Attachment}
ggscatter(finaldt_4, x = "synchrony", y = "PBQ.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Father Postpartum Parental Bonding")
```

```{r Postpartum Synchrony and Maternal Attachment}
linearPostpartumSynchrony_MaternalAttachment <- lm(PBQ.1 ~ synchrony_2, data=finaldt_4)  # build linear regression model on full data
print(linearPostpartumSynchrony_MaternalAttachment)
summary(linearPostpartumSynchrony_MaternalAttachment)
```

```{r Results Postpartum Synchrony and Maternal Attachment}
ggscatter(finaldt_4, x = "synchrony_2", y = "PBQ.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Postpartum Synchrony", ylab = "Mother Postpartum Parental Bonding")
```

```{r Postpartum Synchrony and Paternal Attachment}
linearPostpartumSynchrony_PaternalAttachment <- lm(PBQ.2 ~ synchrony_2, data=finaldt_4)  # build linear regression model on full data
print(linearPostpartumSynchrony_PaternalAttachment)
summary(linearPostpartumSynchrony_PaternalAttachment)
```

```{r Results Postpartum Synchrony and Paternal Attachment}
ggscatter(finaldt_4, x = "synchrony_2", y = "PBQ.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Postpartum Synchrony", ylab = "Paternal Postpartum Parental Bonding")
```

# Synchrony & Parenting Behavior 
```{r Prenatal Synchrony and Maternal Parenting Behavior}
linearPrenatalSynchrony_MaternalParentBehavior <- lm(PARYCtot.1 ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_MaternalParentBehavior)
summary(linearPrenatalSynchrony_MaternalParentBehavior)
```

```{r Graphs Prenatal Synchrony and Maternal Parenting Behavior}
ggscatter(finaldt_4, x = "synchrony", y = "PARYCtot.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Maternal Postpartum Parenting Behavior")
```

```{r Prenatal Synchrony and Paternal Parenting Behavior}
linearPrenatalSynchrony_MaternalParentBehavior <- lm(PARYCtot.2 ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_MaternalParentBehavior)
summary(linearPrenatalSynchrony_MaternalParentBehavior)
```

```{r Results Prenatal Synchrony and Paternal Parenting Behavior}
ggscatter(finaldt_4, x = "synchrony", y = "PARYCtot.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Paternal Postpartum Parenting Behavior")
```

```{r Postpartum Synchrony and Maternal Parenting Behavior}
linearPostpartumSynchrony_PaternalParentBehavior <- lm(PARYCtot.1 ~ synchrony_2, data=finaldt_4)  # build linear regression model on full data
print(linearPostpartumSynchrony_PaternalParentBehavior)
summary(linearPostpartumSynchrony_PaternalParentBehavior)
```

```{r Graph Postpartum Synchrony and Maternal Parenting Behavior}
ggscatter(finaldt_4, x = "synchrony_2", y = "PARYCtot.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Postpartum Synchrony", ylab = "Maternal Postpartum Parenting Behavior")
```

```{r Postpartum Synchrony and Paternal Parenting Behavior}
linearPostpartumSynchrony_PaternalParentBehavior <- lm(PARYCtot.2 ~ synchrony_2, data=finaldt_4)  # build linear regression model on full data
print(linearPostpartumSynchrony_PaternalParentBehavior)
summary(linearPostpartumSynchrony_PaternalParentBehavior)
```

```{r Graph Postpartum Synchrony and Paternal Parenting Behavior}
ggscatter(finaldt_4, x = "synchrony_2", y = "PARYCtot.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Postpartum Synchrony", ylab = "Paternal Postpartum Parenting Behavior")
```

# Synchrony & Relationship Functioning
```{r}
linearPrenatalSynchrony_MaternalRelationship <- lm(DAStotpp.1 ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_MaternalRelationship)
summary(linearPrenatalSynchrony_MaternalRelationship)
```

```{r}
ggscatter(finaldt_4, x = "synchrony", y = "DAStotpp.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Maternal Pospartum Relationship Functioning")
```

```{r Results Prenatal Synchrony and Paternal Relationship}
linearPrenatalSynchrony_PaternalRelationship <- lm(DAStotpp.2 ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_PaternalRelationship)
summary(linearPrenatalSynchrony_PaternalRelationship)
```

```{r Graph Prenatal Synchrony and Paternal Relationship}
ggscatter(finaldt_4, x = "synchrony", y = "DAStotpp.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Paternal Pospartum Relationship Functioning")
```

```{r Postpartum Synchrony and Maternal Relationship}
linearPostpartumSynchrony_MaternalRelationship <- lm(DAStotpp.1 ~ synchrony_2, data=finaldt_4)  # build linear regression model on full data
print(linearPostpartumSynchrony_MaternalRelationship)
summary(linearPostpartumSynchrony_MaternalRelationship)
```

```{r Results Postpartum Synchrony and Maternal Relationship}
ggscatter(finaldt_4, x = "synchrony_2", y = "DAStotpp.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Postpartum Synchrony", ylab = "Maternal Pospartum Relationship Functioning")
```

```{r Postpartum Synchrony and Paternal Relationships}
linearPostpartumSynchrony_PaternalRelationship <- lm(DAStotpp.2 ~ synchrony_2, data=finaldt_4)  # build linear regression model on full data
print(linearPostpartumSynchrony_PaternalRelationship)
summary(linearPostpartumSynchrony_PaternalRelationship)
```

```{r Graph Postpartum Synchrony and Paternal Relationships}
ggscatter(finaldt_4, x = "synchrony_2", y = "DAStotpp.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Postpartum Synchrony", ylab = "Paternal Pospartum Relationship Functioning")
```

```{r s}
finaldt_4 <- finaldt_4 %>% 
  select(CoupID, synchrony, synchrony_2, Age_1.2, bage6pp, everything())
finaldt_4
```


```{r Results Prenatal Synchrony and Prenatal Maternal Relationship}
linearPrenatalSynchrony_MaternalRelationship <- lm(pnDAStot.1 ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_MaternalRelationship)
summary(linearPrenatalSynchrony_MaternalRelationship)
```

```{r Graph Prenatal Synchrony and Prenatal Maternal Relationship}
ggscatter(finaldt_4, x = "synchrony", y = "DAStotpp.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Maternal Pospartum Relationship Functioning")
```

# Synchrony & Marital Satisfaction
```{r Prenatal Synchrony & Prenatal Maternal Marital Satisfaction}
linearPrenatalSynchrony_MaternalRelationshipSat <- lm(pnMaritalSat.1 ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_MaternalRelationshipSat)
summary(linearPrenatalSynchrony_MaternalRelationshipSat)
```

```{r Graph Prenatal Synchrony & Prenatal Maternal Marital Satisfaction}
ggscatter(finaldt_4, x = "synchrony", y = "pnMaritalSat.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Maternal Prenatal Relationship Satisfaction")
```

# Synchrony & Relattionship Functioning
```{r Prenatal Synchrony & Prenatal Paternal Marital Satisfaction}
linearPrenatalSynchrony_PaternalRelationshipSat <- lm(pnMaritalSat.2 ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_PaternalRelationshipSat)
summary(linearPrenatalSynchrony_PaternalRelationshipSat)
```

```{r Graph Prenatal Synchrony & Prenatal Paternal Marital Satisfaction}
ggscatter(finaldt_4, x = "synchrony", y = "pnMaritalSat.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Paternal Prenatal Relationship Satisfaction")
```

```{r Prenatal Synchrony & Postpartum Maternal Marital Satisfaction}
linearPrenatalSynchrony_PaternalRelationshipSat <- lm(MAT1pp ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_PaternalRelationshipSat)
summary(linearPrenatalSynchrony_PaternalRelationshipSat)
```

```{r Graph Prenatal Synchrony & Postpartum Maternal Marital Satisfaction}
ggscatter(finaldt_4, x = "synchrony", y = "MAT1pp", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Maternal Pospartum Relationship Satisfaction")
```

```{r Prenatal Synchrony & Postpartum Paternal Marital Satisfaction}
linearPrenatalSynchrony_PaternalRelationshipSat <- lm(MAT2pp ~ synchrony, data=finaldt_4)  # build linear regression model on full data
print(linearPrenatalSynchrony_PaternalRelationshipSat)
summary(linearPrenatalSynchrony_PaternalRelationshipSat)
```

```{r Graph Prenatal Synchrony & Postpartum Paternal Marital Satisfaction}
ggscatter(finaldt_4, x = "synchrony", y = "MAT2pp", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Paternal Pospartum Relationship Satisfaction")
```

```{r Postpartum Synchrony & Postpartum Maternal Marital Satisfaction}
linearPostpartumSynchrony_MaternalRelationshipSat <- lm(MAT1pp ~ synchrony_2, data=finaldt_4)  # build linear regression model on full data
print(linearPostpartumSynchrony_MaternalRelationshipSat)
summary(linearPostpartumSynchrony_MaternalRelationshipSat)
```

```{r Graph Postpartum Synchrony & Postpartum Maternal Marital Satisfaction}
ggscatter(finaldt_4, x = "synchrony_2", y = "MAT1pp", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Postpartum Synchrony", ylab = "Maternal Pospartum Relationship Satisfaction")
```

```{r Postpartum Synchrony & Postpartum Paternal Marital Satisfaction}
linearPostpartumSynchrony_PaternalRelationshipSat <- lm(MAT2pp ~ synchrony_2, data=finaldt_4)  # build linear regression model on full data
print(linearPostpartumSynchrony_PaternalRelationshipSat)
summary(linearPostpartumSynchrony_PaternalRelationshipSat)
```

```{r Graph Postpartum Synchrony & Postpartum Paternal Marital Satisfaction}
ggscatter(finaldt_4, x = "synchrony_2", y = "MAT2pp", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Postpartum Synchrony", ylab = "Paternal Pospartum Relationship Satisfaction")
```

# Participant descriptives

```{r Age_Mother}
Age_Mother <- stat.desc(finaldt_4$pnAge_1.1)
Age_Mother 
```

```{r Age_Father}
Age_Father <- stat.desc(finaldt_4$pnAge_1.2)
Age_Father
```

```{r Months Pregnant at Prenatal Visit}
monthspreg <- stat.desc(finaldt_4$monthspreg.1)
monthspreg
```

```{r Baby Age at Postpartum Visit}
Baby_age <- stat.desc(finaldt_4$bage6pp.months)
Baby_age
```

```{r Couples_Married or Enengaged }
Couple_RelStat <- table(finaldt_4$RelStat)
Couple_RelStat <- prop.table(Couple_RelStat)
Couple_RelStat
table(finaldt_4$RelStat)
```

```{r Education_Mother}
Education_Mother <- table(finaldt_4$Education.1)
prop.table(Education_Mother)
table(finaldt_4$Education.1)
```

```{r Education_Father}
Education_Father <- table(finaldt_4$Education.2)
prop.table(Education_Father)
table(finaldt_4$Education.2)
```

```{r Ethnicity_Mother}
Ethnicity_Mother <- table(finaldt_4$Ethnicity.1)
prop.table(Ethnicity_Mother)
table(finaldt_4$Ethnicity.1)
```

```{r Ethnicity_Father}
Ethnicity_Father <-table(finaldt_4$Ethnicity.2)
prop.table(Ethnicity_Father)
table(finaldt_4$Ethnicity.2)
```
# Descriptive Statistics of Self-Reported Measuress

```{r Testosterone_Prenatal_Mother}
Testosterone_Prenatal_Mother <- stat.desc(Long_finaldt_4$Mompn)
Testosterone_Prenatal_Mother
```

```{r Testosterone_Prenatal_Father}
Testosterone_Prenatal_Father <- stat.desc(Long_finaldt_4$Dadpn)
Testosterone_Prenatal_Father
```

```{r Testosterone_Postpartuml_Mother}
Testosterone_Postpartuml_Mother <- stat.desc(Long_finaldt_4$Mompp)
Testosterone_Postpartuml_Mother
```

```{r Testosterone_Postpartuml_Father}
Testosterone_Postpartuml_Father <- stat.desc(Long_finaldt_4$Dadpp)
Testosterone_Postpartuml_Father
```

```{r Testosterone Change Father}
Testosterone_Change_Father <- stat.desc(df_WIDE$Dad_Change)
Testosterone_Change_Father
```


```{r Mother Postpartum Relationship Functioning}
Relationship_Satisfaction_Postpartum_Mother <- stat.desc(finaldt_4$DAStotpp.1)
Relationship_Satisfaction_Postpartum_Mother
```

```{r Father Postpartum Relationship Functioning}
Relationship_Satisfaction_Postpartum_Father <- stat.desc(finaldt_4$DAStotpp.2)
Relationship_Satisfaction_Postpartum_Father
```

```{r Mother Postpartum Marital Satisfaction}
Marital_Satisfaction_Postpartum_Mother <- stat.desc(finaldt_4$MAT1pp)
Marital_Satisfaction_Postpartum_Mother
```

```{r Father Postpartum Marital Satisfaction}
Marital_Satisfaction_Postpartum_Father <- stat.desc(finaldt_4$MAT2pp)
Marital_Satisfaction_Postpartum_Father
```

```{r Mother Postpartum Parenting Behavior}
Parenting_Behavior_Postpartum_Mother <- stat.desc(finaldt_4$PARYCtot.1)
Parenting_Behavior_Postpartum_Mother
```

```{r Father Postpartum Parenting Behavior}
Parenting_Behavior_Postpartum_Father <- stat.desc(finaldt_4$PARYCtot.2)
Parenting_Behavior_Postpartum_Father
```

```{r Mother Postpartum Bonding}
Bonding_Postpartum_Mother <- stat.desc(finaldt_4$PBQ.1)
Bonding_Postpartum_Mother
```

```{r Father Postpartum Bonding}
Bonding_Postpartum_Father <- stat.desc(finaldt_4$PBQ.2)
Bonding_Postpartum_Father
```

# Preliminary analyses of the hormones

```{r Wide Data to Long Format}
# Using the new `tidyr::pivot_longer()` function
Long_finaldt_4 <- finaldt_4 %>% 
  pivot_longer(
    c(Mompn1:Mompn3, Dadpn1:Dadpn3, Mompp1:Mompp3, Dadpp1:Dadpp3), # variables that are repeated measures
    # Convert 8 columns to 3: 2 columns each for anti/read (.value), and 
    # one column for time
    names_to = c(".value", "Testo_Measurement"),
    # Extract the names "anti"/"read" from the names of the variables for the 
    # value columns, and then the number to the "time" column
    names_pattern = "(Mompn|Dadpn|Mompp|Dadpp)([1-3])", 
    # Convert the "time" column to integers
    names_transform = list(time = as.integer)
    )
Long_finaldt_4 %>% 
  select(CoupID, Testo_Measurement, Mompn, Dadpn, Mompp, Dadpp, everything())
```

```{r}
Long_finaldt_4 <- Long_finaldt_4 %>% 
    mutate(Dad_Change = DadTesto1 - DadTesto2)
```

```{r}
df_LONG_2 <- read.spss('/Users/sofiacardenas/Desktop/MLM(psyc575)/Final_Project/HATCH_12.10.2020.sav', use.value.label=TRUE, to.data.frame=TRUE)
```

```{r Second Convert Wide Data to Long Format to see pre and post changes in time points}
# Using the new `tidyr::pivot_longer()` function
df_LONG_2 <- finaldt_4 %>% 
  pivot_longer(
    c(MomTesto1:DadTesto2), # variables that are repeated measures
    names_to = c(".value", "Visit"),
    # Extract the names "anti"/"read" from the names of the variables for the 
    # value columns, and then the number to the "time" column
    names_pattern = "(DadTesto|MomTesto)([1-2])", 
    # Convert the "time" column to integers
    names_transform = list(Visit = as.integer)
  )
df_LONG_2 %>% 
  select(CoupID, DadTesto, MomTesto, Visit, Dad_Change, everything())
```

```{r Analyses_Repeated measure anova Mom x Pre x Time}
summary(aov(Mompn ~ Testo_Measurement, data=Long_finaldt_4))
```

```{r Figure_Mom testosterone during prenatal visit}
ggline(Long_finaldt_4, x = "Testo_Measurement", y = "Mompn", 
       add = c("mean_se", "jitter"), 
       order = c("1", "2", "3"),
       ylab = "Mothers' Prenatal Testosterone", xlab = "Prenatal Testosterone Measurements")
```

```{r Analyses_Repeated measure anova Dad x Pre x Time}
summary(aov(Dadpn ~ Testo_Measurement, data=Long_finaldt_4))
```

```{r Figure_Dad testosterone during prenatal visit}
ggline(Long_finaldt_4, x = "Testo_Measurement", y = "Dadpn", 
       add = c("mean_se", "jitter"), 
       order = c("1", "2", "3"),
       ylab = "Fathers' Prenatal Testosterone", xlab = "Prenatal Testosterone Measurements")
```

```{r ANOVA of Dadpn and Time}
pairwise.t.test(Long_finaldt_4$Dadpn, Long_finaldt_4$Testo_Measurement, p.adj = "none", data=Long_finaldt_4)
```

```{r T-test of fathers 2nd and 3rd prenatal time points}
# paired t-test
Sec_Thir_pn_Test <- t.test(finaldt_4$Dadpn2,finaldt_4$Dadpn3,paired=TRUE,na.action = na.omit) # where y1 & y2 are numeric
``` 

```{r Result in T-test of fathers 2nd and 3rd prenatal time points}
Sec_Thir_pn_Test
```


```{r Analyses_Repeated measure anova Mom x Post x Time}
summary(aov(Mompp ~ Testo_Measurement, data=Long_finaldt_4))
```

```{r Figure_Mom testosterone during postpartum visit}
ggline(Long_finaldt_4, x = "Testo_Measurement", y = "Mompp", 
       add = c("mean_se", "jitter"), 
       order = c("1", "2", "3"),
       ylab = "Mothers' Postpartum Testosterone", xlab = "Postpartum Testosterone Measurements")
```

```{r Analyses_Repeated measure anova Dad x Post x Time}
summary(aov(Dadpp ~ Testo_Measurement, data=Long_finaldt_4))
```

```{r Analyses_Figure_Dad testosterone during prenatal visit}
ggline(Long_finaldt_4, x = "Testo_Measurement", y = "Dadpp", 
       add = c("mean_se", "jitter"), 
       order = c("1", "2", "3"),
       ylab = "Fathers' Postpartum Testosterone", xlab = "Postpartum Testosterone Measurements")
```

```{r T-test of mothers prenatal to postpartum testosterone}
# paired t-test
Mom_change <- t.test(Long_finaldt_4$MomTesto1,Long_finaldt_4$MomTesto2,paired=TRUE,na.action = na.omit) # where y1 & y2 are numeric
``` 

```{r Result in T-test of mothers prenatal to postpartum testosterone}
Mom_change
```

```{r Bar graph of female prenatal and postpartum testosterone}
# First distribution
hist(Long_finaldt_4$MomTesto1, breaks=5, xlim=c(0,55), col=rgb(1,0,0,0.5), xlab="Testosterone Level", 
     ylab="Frequency", main="Mothers' Prenatal and Postpatum Testosterone" )

# Second with add=T to plot on top
hist(Long_finaldt_4$MomTesto2, breaks=5, xlim=c(0,55), col=rgb(0,0,1,0.5), add=T)

# Add legend
legend("topright", legend=c("Prenatal","Postpartum"), col=c(rgb(1,0,0,0.5), 
     rgb(0,0,1,0.5)), pt.cex=2, pch=15 )
```

```{r Spaghetti of female prenatal and postpartum testosterone}
# Female' Prenatal and Postpartum Testosterone
Spaghettiogram(MomTesto~Visit+id(CoupID),
               data=df_LONG_2,
               xlim=c(.5, 3),
               axis1.at=c(1,2), ylab="Female Testosterone",
               axis1.lab=c("Prenatal","Postpartum"))
```

```{r T-test male prenatal and postpartum testosterone}
# paired t-test
Dad_change <- t.test(Long_finaldt_4$DadTesto1,Long_finaldt_4$DadTesto2,paired=TRUE,na.action = na.omit) 
``` 

```{r}
Dad_change
```

```{r Bar graph of male prenatal and postpartum testosterone}
# First distribution
hist(Long_finaldt_4$DadTesto1, breaks=10, xlim=c(0,150), col=rgb(1,0,0,0.5), xlab="Testosterone Level", 
     ylab="Frequency", main="Fathers' Prenatal and Postpatum Testosterone" )

# Second with add=T to plot on top
hist(Long_finaldt_4$DadTesto2, breaks=10, xlim=c(0,150), col=rgb(0,0,1,0.5), add=T)

# Add legend
legend("topright", legend=c("Prenatal","Postpartum"), col=c(rgb(1,0,0,0.5), 
     rgb(0,0,1,0.5)), pt.cex=2, pch=15 )
```

```{r Spaghetti of male prenatal and postpartum testosterone}
# Males' Prenatal and Postpartum Testosterone
Spaghettiogram(DadTesto~Visit+id(CoupID),
               data=df_LONG_2,
               xlim=c(.5, 3),
               axis1.at=c(1,2), ylab="Male Testosterone",
               axis1.lab=c("Prenatal","Postpartum"))
```

# Correlation of main study variables

```{r 1. Mothers’ Age X 2. Fathers’ Age}
One.Two <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$pnAge_1.2,use ="complete.obs", method = "pearson")
One.Two
```

```{r 1. Mothers’ Age X 3. Months Pregnant}
One.Three <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$monthspreg.1,use = "complete.obs", method = "pearson")
One.Three
```

```{r 1. Mothers’ Age X 4. Baby Age}
One.Four <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$bage6pp.months,use = "complete.obs", method = "pearson")
One.Four
```

```{r 1. Mothers’ Age X 5. PN TestosteroneMom}
One.Five <- cor.test(Long_finaldt_4$pnAge_1.1,Long_finaldt_4$Mompn,use = "complete.obs", method = "pearson")
One.Five
```

```{r 1. Mothers’ Age X 6. PN TestosteroneDad}
One.Six <- cor.test(Long_finaldt_4$pnAge_1.1,Long_finaldt_4$Dadpn,use = "complete.obs", method = "pearson")
One.Six
```

```{r 1. Mothers’ Age X 7. PP TestosteroneMom}
One.Seven <- cor.test(Long_finaldt_4$pnAge_1.1,Long_finaldt_4$Mompp,use = "complete.obs", method = "pearson")
One.Seven
```

```{r 1. Mothers’ Age X 8. Change TestosteroneDad}
One.Eight <- cor.test(Long_finaldt_4$pnAge_1.1,Long_finaldt_4$Dadpp,use = "complete.obs", method = "pearson")
One.Eight
```

```{r 1. Mothers’ Age X 9.	PP TestosteroneDad}
One.Nine <- cor.test(df_WIDE$pnAge_1.1,df_WIDE$Dad_Change,use = "complete.obs", method = "pearson")
One.Nine
```

```{r 1. Mothers’ Age X 10. PP Relationship FunctioningMom}
One.Ten <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$DAStotpp.1,use = "complete.obs", method = "pearson")
One.Ten
```

```{r 1. Mothers’ Age X 11. PP Relationship FunctioningDad}
One.Eleven <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$DAStotpp.2,use = "complete.obs", method = "pearson")
One.Eleven
```

```{r 1. Mothers’ Age X 12. PP Relationship SatisfactionMom}
One.Twelve <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$MAT1pp,use = "complete.obs", method = "pearson")
One.Twelve
```

```{r 1. Mothers’ Age X 13. PP Relationship SatisfactionDad}
One.Thirteen <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$MAT2pp,use = "complete.obs", method = "pearson")
One.Thirteen
```

```{r 1. Mothers’ Age X 14. PP ParentingMom}
One.Fourteen <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
One.Fourteen
```

```{r 1. Mothers’ Age X  15. PP ParentingDad}
One.Fifteen <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
One.Fifteen
```

```{r 1. Mothers’ Age X 16. Postpartum BondingMom}
One.Sixteen <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
One.Sixteen 
```

```{r 1. Mothers’ Age X 17. Postpartum BondingDad}
One.Seventeen <- cor.test(finaldt_4$pnAge_1.1,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
One.Seventeen
```

```{r 2. Fathers’ Age (PN) X 3. Months Pregnant}
Two.Three <- cor.test(finaldt_4$pnAge_1.2,finaldt_4$monthspreg.1,use = "complete.obs", method = "pearson")
Two.Three
```

```{r 2. Fathers’ Age (PN) X 4. Baby Age}
Two.Four <- cor.test(finaldt_4$pnAge_1.2,finaldt_4$bage6pp.months,use = "complete.obs", method = "pearson")
Two.Four
```

```{r 2. Fathers’ Age (PN) X 5. PN TestosteroneMom}
Two.Five <- cor.test(Long_finaldt_4$pnAge_1.2,Long_finaldt_4$Mompn,use = "complete.obs", method = "pearson")
Two.Five
```

```{r 2. Fathers’ Age (PN) X 6. PN TestosteroneDad}
Two.Six <- cor.test(Long_finaldt_4$pnAge_1.2,Long_finaldt_4$Dadpn,use = "complete.obs", method = "pearson")
Two.Six
```

```{r 2. Fathers’ Age (PN) X 7. PP TestosteroneMom}
Two.Seven <- cor.test(Long_finaldt_4$pnAge_1.2,Long_finaldt_4$Mompp,use = "complete.obs", method = "pearson")
Two.Seven
```

```{r 2. Fathers’ Age (PN) X 8. Change TestosteroneDad}
Two.Eight <- cor.test(Long_finaldt_4$pnAge_1.2,Long_finaldt_4$Dadpp,use = "complete.obs", method = "pearson")
Two.Eight
```

```{r 2. Fathers’ Age (PN) X 9.	PP TestosteroneDad}
Two.Nine <- cor.test(df_WIDE$pnAge_1.2,df_WIDE$Dad_Change,use = "complete.obs", method = "pearson")
Two.Nine
```

```{r 2. Fathers’ Age (PN) X 10. PP Relationship FunctioningMom}
Two.Ten <- cor.test(finaldt_4$pnAge_1.2,finaldt_4$DAStotpp.1,use = "complete.obs", method = "pearson")
Two.Ten
```

```{r 2. Fathers’ Age (PN) X 11. PP Relationship FunctioningDad}
Two.Eleven <- cor.test(finaldt_4$pnAge_1.2,finaldt_4$DAStotpp.2,use = "complete.obs", method = "pearson")
Two.Eleven
```

```{r 2. Fathers’ Age (PN) X 12. PP Relationship SatisfactionMom}
Two.Twelve <- cor.test(finaldt_4$pnAge_1.2,finaldt_4$MAT1pp,use = "complete.obs", method = "pearson")
Two.Twelve
```

```{r 2. Fathers’ Age (PN) X 13. PP Relationship SatisfactionDad}
Two.Thirteen <- cor.test(finaldt_4$pnAge_1.2,finaldt_4$MAT2pp,use = "complete.obs", method = "pearson")
Two.Thirteen
```

```{r 2. Fathers’ Age (PN) X 14. PP ParentingMom}
Two.Fourteen <- cor.test(finaldt_4$pnAge_1.2,finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Two.Fourteen
```

```{r 2. Fathers’ Age (PN) X  15. PP ParentingDad}
Two.Fifteen <- cor.test(finaldt_4$pnAge_1.2,finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Two.Fifteen
```

```{r 2. Fathers’ Age (PN) X 16. Postpartum BondingMom}
Two.Sixteen <- cor.test(finaldt_4$pnAge_1.2,finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Two.Sixteen 
```

```{r 2. Fathers’ Age (PN) X 17. Postpartum BondingDad}
Two.Seventeen <- cor.test(finaldt_4$pnAge_1.2,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Two.Seventeen
```

```{r 3. Months Pregnant (PN) X 4. Baby Age}
Three.Four <- cor.test(finaldt_4$monthspreg.1,finaldt_4$bage6pp.months,use = "complete.obs", method = "pearson")
Three.Four
```

```{r 3. Months Pregnant (PN) X 5. PN TestosteroneMom}
Three.Five <- cor.test(Long_finaldt_4$monthspreg.1,Long_finaldt_4$Mompn,use = "complete.obs", method = "pearson")
Three.Five
```

```{r 3. Months Pregnant (PN) X 6. PN TestosteroneDad}
Three.Six <- cor.test(Long_finaldt_4$monthspreg.1,Long_finaldt_4$Dadpn,use = "complete.obs", method = "pearson")
Three.Six
```

```{r 3. Months Pregnant (PN) X 7. PP TestosteroneMom}
Three.Seven <- cor.test(Long_finaldt_4$monthspreg.1,Long_finaldt_4$Mompp,use = "complete.obs", method = "pearson")
Three.Seven
```

```{r 3. Months Pregnant (PN) X 8. Change TestosteroneDad}
Three.Eight <- cor.test(Long_finaldt_4$monthspreg.1,Long_finaldt_4$Dadpp,use = "complete.obs", method = "pearson")
Three.Eight
```

```{r 3. Months Pregnant (PN) X 9.	PP TestosteroneDad}
Three.Nine <- cor.test(df_WIDE$monthspreg.1,df_WIDE$Dad_Change,use = "complete.obs", method = "pearson")
Three.Nine
```

```{r 3. Months Pregnant (PN) X 10. PP Relationship FunctioningMom}
Three.Ten <- cor.test(finaldt_4$monthspreg.1,finaldt_4$DAStotpp.1,use = "complete.obs", method = "pearson")
Three.Ten
```

```{r 3. Months Pregnant (PN) X 11. PP Relationship FunctioningDad}
Three.Eleven <- cor.test(finaldt_4$monthspreg.1,finaldt_4$DAStotpp.2,use = "complete.obs", method = "pearson")
Three.Eleven
```

```{r 3. Months Pregnant (PN) X 12. PP Relationship SatisfactionMom}
Three.Twelve <- cor.test(finaldt_4$monthspreg.1,finaldt_4$MAT1pp,use = "complete.obs", method = "pearson")
Three.Twelve
```

```{r 3. Months Pregnant (PN) X 13. PP Relationship SatisfactionDad}
Three.Thirteen <- cor.test(finaldt_4$monthspreg.1,finaldt_4$MAT2pp,use = "complete.obs", method = "pearson")
Three.Thirteen
```

```{r 3. Months Pregnant (PN) X 14. PP ParentingMom}
Three.Fourteen <- cor.test(finaldt_4$monthspreg.1,finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Three.Fourteen
```

```{r 3. Months Pregnant (PN) X  15. PP ParentingDad}
Three.Fifteen <- cor.test(finaldt_4$monthspreg.1,finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Three.Fifteen
```

```{r 3. Months Pregnant (PN) X 16. Postpartum BondingMom}
Three.Sixteen <- cor.test(finaldt_4$monthspreg.1,finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Three.Sixteen 
```

```{r 3. Months Pregnant (PN) X 17. Postpartum BondingDad}
Three.Seventeen <- cor.test(finaldt_4$monthspreg.1,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Three.Seventeen
```

```{r 4. Baby Age (PP) X 5. PN TestosteroneMom}
Four.Five <- cor.test(Long_finaldt_4$bage6pp.months,Long_finaldt_4$Mompn,use = "complete.obs", method = "pearson")
Four.Five
```

```{r 4. Baby Age (PP) X 6. PN TestosteroneDad}
Four.Six <- cor.test(Long_finaldt_4$bage6pp.months,Long_finaldt_4$Dadpn,use = "complete.obs", method = "pearson")
Four.Six
```

```{r 4. Baby Age (PP) X 7. PP TestosteroneMom}
Four.Seven <- cor.test(Long_finaldt_4$bage6pp.months,Long_finaldt_4$Mompp,use = "complete.obs", method = "pearson")
Four.Seven
```

```{r 4. Baby Age (PP) X 8. Change TestosteroneDad}
Four.Eight <- cor.test(Long_finaldt_4$bage6pp.months,Long_finaldt_4$Dadpp,use = "complete.obs", method = "pearson")
Four.Eight
```

```{r 4. Baby Age (PP) X 9.	PP TestosteroneDad}
Four.Nine <- cor.test(df_WIDE$bage6pp.months,df_WIDE$Dad_Change,use = "complete.obs", method = "pearson")
Four.Nine
```

```{r 4. Baby Age (PP) X 10. PP Relationship FunctioningMom}
Four.Ten <- cor.test(finaldt_4$bage6pp.months,finaldt_4$DAStotpp.1,use = "complete.obs", method = "pearson")
Four.Ten
```

```{r 4. Baby Age (PP) X 11. PP Relationship FunctioningDad}
Four.Eleven <- cor.test(finaldt_4$bage6pp.months,finaldt_4$DAStotpp.2,use = "complete.obs", method = "pearson")
Four.Eleven
```

```{r 4. Baby Age (PP) X 12. PP Relationship SatisfactionMom}
Four.Twelve <- cor.test(finaldt_4$bage6pp.months,finaldt_4$MAT1pp,use = "complete.obs", method = "pearson")
Four.Twelve
```

```{r 4. Baby Age (PP) X 13. PP Relationship SatisfactionDad}
Four.Thirteen <- cor.test(finaldt_4$bage6pp.months,finaldt_4$MAT2pp,use = "complete.obs", method = "pearson")
Four.Thirteen
```

```{r 4. Baby Age (PP) X 14. PP ParentingMom}
Four.Fourteen <- cor.test(finaldt_4$bage6pp.months,finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Four.Fourteen
```

```{r 4. Baby Age (PP) X  15. PP ParentingDad}
Four.Fifteen <- cor.test(finaldt_4$bage6pp.months,finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Four.Fifteen
```

```{r 4. Baby Age (PP) X 16. Postpartum BondingMom}
Four.Sixteen <- cor.test(finaldt_4$bage6pp.months,finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Four.Sixteen 
```

```{r 4. Baby Age (PP) X 17. Postpartum BondingDad}
Four.Seventeen <- cor.test(finaldt_4$bage6pp.months,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Four.Seventeen
```

```{r 5. PN TestosteroneMomX 6. PN TestosteroneDad}
Five.Six <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$Dadpn,use = "complete.obs", method = "pearson")
Five.Six
```

```{r 5. PN TestosteroneMomX 7. PP TestosteroneMom}
Five.Seven <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$Mompp,use = "complete.obs", method = "pearson")
Five.Seven
```

```{r 5. PN TestosteroneMomX 8. Change TestosteroneDad}
Five.Eight <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$Dadpp,use = "complete.obs", method = "pearson")
Five.Eight
```

```{r 5. PN TestosteroneMomX 9.	PP TestosteroneDad}
Five.Nine <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$Dad_Change, use = "complete.obs", method = "pearson")
Five.Nine
```

```{r 5. PN TestosteroneMomX 10. PP Relationship FunctioningMom}
Five.Ten <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$DAStotpp.1, use = "complete.obs", method = "pearson")
Five.Ten
```

```{r 5. PN TestosteroneMomX 11. PP Relationship FunctioningDad}
Five.Eleven <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$DAStotpp.2,use = "complete.obs", method = "pearson")
Five.Eleven
```

```{r 5. PN TestosteroneMomX 12. PP Relationship SatisfactionMom}
Five.Twelve <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$MAT1pp,use = "complete.obs", method = "pearson")
Five.Twelve
```

```{r 5. PN TestosteroneMomX 13. PP Relationship SatisfactionDad}
Five.Thirteen <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$MAT2pp,use = "complete.obs", method = "pearson")
Five.Thirteen
```

```{r 5. PN TestosteroneMomX 14. PP ParentingMom}
Five.Fiveteen <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Five.Fiveteen
```

```{r 5. PN TestosteroneMomX  15. PP ParentingDad}
Five.Fifteen <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Five.Fifteen
```

```{r 5. PN TestosteroneMomX 16. Postpartum BondingMom}
Five.Sixteen <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Five.Sixteen 
```

```{r 5. PN TestosteroneMomX 17. Postpartum BondingDad}
Five.Seventeen <- cor.test(Long_finaldt_4$Mompn,Long_finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Five.Seventeen
```

```{r 6. PN TestosteroneDadX 7. PP TestosteroneMom}
Six.Seven <- cor.test(Long_finaldt_4$Dadpn,Long_finaldt_4$Mompp,use = "complete.obs", method = "pearson")
Six.Seven
```

```{r 6. PN TestosteroneDadX 8. Change TestosteroneDad}
Six.Eight <- cor.test(Long_finaldt_4$Dadpn,Long_finaldt_4$Dadpp,use = "complete.obs", method = "pearson")
Six.Eight
```

```{r 6. PN TestosteroneDadX 9.PP TestosteroneDad}
Six.Nine <- cor.test(df_WIDE$bage6pp.months,df_WIDE$Dad_Change,use = "complete.obs", method = "pearson")
Six.Nine 
```

```{r 6. PN TestosteroneDadX 10. PP Relationship FunctioningMom}
Six.Ten <- cor.test(Long_finaldt_4$Dadpn,Long_finaldt_4$DAStotpp.1,use = "complete.obs", method = "pearson")
Six.Ten 
```

```{r 6. PN TestosteroneDadX 11. PP Relationship FunctioningDad}
Six.Eleven <- cor.test(Long_finaldt_4$Dadpn,Long_finaldt_4$DAStotpp.2,use = "complete.obs", method = "pearson")
Six.Eleven 
```

```{r 6. PN TestosteroneDadX 12. PP Relationship SatisfactionMom}
Six.Twelve <- cor.test(Long_finaldt_4$Dadpn,Long_finaldt_4$MAT1pp,use = "complete.obs", method = "pearson")
Six.Twelve 
```

```{r 6. PN TestosteroneDadX 13. PP Relationship SatisfactionDad}
Six.Thirteen <- cor.test(Long_finaldt_4$Dadpn,Long_finaldt_4$MAT2pp,use = "complete.obs", method = "pearson")
Six.Thirteen 
```

```{r 6. PN TestosteroneDadX 14. PP ParentingMom}
Six.Seventeen <- cor.test(Long_finaldt_4$Dadpn,Long_finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Six.Seventeen 
```

```{r 6. PN TestosteroneDadX  15. PP ParentingDad}
Six.Fifteen <- cor.test(Long_finaldt_4$Dadpn,Long_finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Six.Fifteen
```

```{r 6. PN TestosteroneDadX 16. Postpartum BondingMom}
Six.Sixteen <- cor.test(Long_finaldt_4$Dadpn,Long_finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Six.Sixteen
```

```{r 6. PN TestosteroneDadX 17. Postpartum BondingDad}
Six.Seventeen <- cor.test(Long_finaldt_4$Dadpn,Long_finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Six.Seventeen 
```


```{r 7. PP TestosteroneMom X 8.PP TestosteroneDad}
Seven.Eight <- cor.test(Long_finaldt_4$Mompp,Long_finaldt_4$Dadpp,use = "complete.obs", method = "pearson")
Seven.Eight
```

```{r 7. PP TestosteroneMom X 9.Change TestosteroneDad}
Seven.Nine <- cor.test(df_WIDE$bage6pp.months,df_WIDE$Dad_Change,use = "complete.obs", method = "pearson")
Seven.Nine
```

```{r 7. PP TestosteroneMom X 10. PP Relationship FunctioningMom}
Seven.Ten <- cor.test(Long_finaldt_4$Mompp,Long_finaldt_4$DAStotpp.1,use = "complete.obs", method = "pearson")
Seven.Ten
```

```{r 7. PP TestosteroneMom X 11. PP Relationship FunctioningDad}
Seven.Eleven <- cor.test(Long_finaldt_4$Mompp,Long_finaldt_4$DAStotpp.2,use = "complete.obs", method = "pearson")
Seven.Eleven
```

```{r 7. PP TestosteroneMom X 12. PP Relationship SatisfactionMom}
Seven.Twelve <- cor.test(Long_finaldt_4$Mompp,Long_finaldt_4$MAT1pp,use = "complete.obs", method = "pearson")
Seven.Twelve
```

```{r 7. PP TestosteroneMom X 13. PP Relationship SatisfactionDad}
Seven.Thirteen <- cor.test(Long_finaldt_4$Mompp,Long_finaldt_4s$MAT2pp,use = "complete.obs", method = "pearson")
Seven.Thirteen
```

```{r 7. PP TestosteroneMom X 14. PP ParentingMom}
Seven.Seventeen <- cor.test(Long_finaldt_4$Mompp,Long_finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Seven.Seventeen
```

```{r 7. PP TestosteroneMom X  15. PP ParentingDad}
Seven.Fifteen <- cor.test(Long_finaldt_4$Mompp,Long_finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Seven.Fifteen
```

```{r 7. PP TestosteroneMom X 16. Postpartum BondingMom}
Seven.Sixteen <- cor.test(Long_finaldt_4$Mompp,Long_finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Seven.Sixteen 
```

```{r 7. PP TestosteroneMom X 17. Postpartum BondingDad}
Seven.Seventeen <- cor.test(Long_finaldt_4$Mompp,Long_finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Seven.Seventeen
```


```{r 8. PP TestosteroneDad 9.PP TestosteroneDad}
Eight.Nine <- cor.test(Long_finaldt_4$Dadpp,Long_finaldt_4$Dad_Change,use = "complete.obs", method = "pearson")
Eight.Nine 
```

```{r 8. PP TestosteroneDad 10. PP Relationship FunctioningMom}
Eight.Ten <- cor.test(Long_finaldt_4$Dadpp,Long_finaldt_4$DAStotpp.1,use = "complete.obs", method = "pearson")
Eight.Ten 
```

```{r 8. PP TestosteroneDad 11. PP Relationship FunctioningDad}
Eight.Eleven <- cor.test(Long_finaldt_4$Dadpp,Long_finaldt_4$DAStotpp.2,use = "complete.obs", method = "pearson")
Eight.Eleven 
```

```{r 8. PP TestosteroneDad 12. PP Relationship SatisfactionMom}
Eight.Twelve <- cor.test(Long_finaldt_4$Dadpp,Long_finaldt_4$MAT1pp,use = "complete.obs", method = "pearson")
Eight.Twelve 
```

```{r 8. PP TestosteroneDad 13. PP Relationship SatisfactionDad}
Eight.Thirteen <- cor.test(Long_finaldt_4$Dadpp,Long_finaldt_4$MAT2pp,use = "complete.obs", method = "pearson")
Eight.Thirteen 
```

```{r 8. PP TestosteroneDad 14. PP ParentingMom}
Eight.Fourteen <- cor.test(Long_finaldt_4$Dadpp,Long_finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Eight.Fourteen
```

```{r 8. PP TestosteroneDad  15. PP ParentingDad}
Eight.Fifteen <- cor.test(Long_finaldt_4$Dadpp,Long_finaldt_4s$PARYCtot.2,use = "complete.obs", method = "pearson")
Eight.Fifteen
```

```{r 8. PP TestosteroneDad 16. Postpartum BondingMom}
Eight.Sixteen <- cor.test(Long_finaldt_4$Dadpp,Long_finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Eight.Sixteen
```

```{r 8. PP TestosteroneDad 17. Postpartum BondingDad}
Eight.Seventeen <- cor.test(Long_finaldt_4$Dadpp,Long_finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Eight.Seventeen 
```

```{r 9. Change TestosteroneDad X 10. PP Relationship FunctioningMom}
Nine.Ten <- cor.test(df_WIDE$Dad_Change,df_WIDE$DAStotpp.1,use = "complete.obs", method = "pearson")
Nine.Ten 
```

```{r 9. Change TestosteroneDad X 11. PP Relationship FunctioningDad}
Nine.Eleven <- cor.test(df_WIDE$Dad_Change,df_WIDE$DAStotpp.2,use = "complete.obs", method = "pearson")
Nine.Eleven 
```

```{r 9. Change TestosteroneDad X 12. PP Relationship SatisfactionMom}
Nine.Twelve <- cor.test(df_WIDE$Dad_Change,df_WIDE$MAT1pp,use = "complete.obs", method = "pearson")
Nine.Twelve 
```

```{r 9. Change TestosteroneDad X 13. PP Relationship SatisfactionDad}
Nine.Thirteen <- cor.test(df_WIDE$Dad_Change,df_WIDE$MAT2pp,use = "complete.obs", method = "pearson")
Nine.Thirteen 
```

```{r 9. Change TestosteroneDad X 14. PP ParentingMom}
Nine.Seventeen <- cor.test(df_WIDE$Dad_Change,df_WIDE$PARYCtot.1,use = "complete.obs", method = "pearson")
Nine.Seventeen 
```

```{r 9. Change TestosteroneDad X  15. PP ParentingDad}
Nine.Fifteen <- cor.test(df_WIDE$Dad_Change,df_WIDE$PARYCtot.2,use = "complete.obs", method = "pearson")
Nine.Fifteen
```

```{r 9. Change TestosteroneDad X 16. Postpartum BondingMom}
Nine.Eightteen <- cor.test(df_WIDE$Dad_Change,df_WIDE$PBQ.1,use = "complete.obs", method = "pearson")
Nine.Eightteen
```

```{r 9. Change TestosteroneDad X 17. Postpartum BondingDad}
Nine.Seventeen <- cor.test(df_WIDE$Dad_Change,df_WIDE$PBQ.2 ,use = "complete.obs", method = "pearson")
Nine.Seventeen 
```

```{r 10. PP Relationship FunctioningMom X 11. PP Relationship FunctioningDad}
Ten.Eleven <- cor.test(df_WIDE$DAStotpp.1,df_WIDE$DAStotpp.2,use = "complete.obs", method = "pearson")
Ten.Eleven 
```

```{r 10. PP Relationship FunctioningMom X 12. PP Relationship SatisfactionMom}
Ten.Twelve <- cor.test(df_WIDE$DAStotpp.1,df_WIDE$MAT1pp,use = "complete.obs", method = "pearson")
Ten.Twelve 
```

```{r 10. PP Relationship FunctioningMom X 13. PP Relationship SatisfactionDad}
Ten.Thirteen <- cor.test(finaldt_4$DAStotpp.1,finaldt_4$MAT2pp,use = "complete.obs", method = "pearson")
Ten.Thirteen 
```

```{r 10. PP Relationship FunctioningMom X 14. PP ParentingMom}
Ten.Seventeen <- cor.test(finaldt_4$DAStotpp.1,finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Ten.Seventeen 
```

```{r 10. PP Relationship FunctioningMom X  15. PP ParentingDad}
Ten.Fifteen <- cor.test(finaldt_4$DAStotpp.1,finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Ten.Fifteen
```

```{r 10. PP Relationship FunctioningMom X 16. Postpartum BondingMom}
Ten.Eightteen <- cor.test(finaldt_4$DAStotpp.1,finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Ten.Eightteen
```

```{r 10. PP Relationship FunctioningMom X 17. Postpartum BondingDad}
Ten.Seventeen <- cor.test(finaldt_4$DAStotpp.1,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Ten.Seventeen 
```

```{r 11. PP Relationship FunctioningDad X 12. PP Relationship SatisfactionMom}
Eleven.Twelve <- cor.test(finaldt_4$DAStotpp.2,finaldt_4$MAT1pp,use = "complete.obs", method = "pearson")
Eleven.Twelve 
```

```{r 11. PP Relationship FunctioningDad X 13. PP Relationship SatisfactionDad}
Eleven.Thirteen <- cor.test(finaldt_4$DAStotpp.2,finaldt_4$MAT2pp,use = "complete.obs", method = "pearson")
Eleven.Thirteen 
```

```{r 11. PP Relationship FunctioningDad X 14. PP ParentingMom}
Eleven.Seventeen <- cor.test(finaldt_4$DAStotpp.2,finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Eleven.Seventeen 
```

```{r 11. PP Relationship FunctioningDad X  15. PP ParentingDad}
Eleven.Fifteen <- cor.test(finaldt_4$DAStotpp.2,finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Eleven.Fifteen
```

```{r 11. PP Relationship FunctioningDad X 16. Postpartum BondingMom}
Eleven.Eightteen <- cor.test(finaldt_4$DAStotpp.2,finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Eleven.Eightteen
```

```{r 11. PP Relationship FunctioningDad X 17. Postpartum BondingDad}
Eleven.Seventeen <- cor.test(finaldt_4$DAStotpp.2,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Eleven.Seventeen 
```

```{r 12. PP Relationship SatisfactionMom X 13. PP Relationship SatisfactionDad}
Twelve.Thirteen <- cor.test(finaldt_4$MAT1pp,finaldt_4$MAT2pp,use = "complete.obs", method = "pearson")
Twelve.Thirteen 
```

```{r 12. PP Relationship SatisfactionMom X 14. PP ParentingMom}
Twelve.Seventeen <- cor.test(finaldt_4$MAT1pp,finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Twelve.Seventeen 
```

```{r 12. PP Relationship SatisfactionMom X  15. PP ParentingDad}
Twelve.Fifteen <- cor.test(finaldt_4$MAT1pp,finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Twelve.Fifteen
```

```{r 12. PP Relationship SatisfactionMom X 16. Postpartum BondingMom}
Twelve.Eightteen <- cor.test(finaldt_4$MAT1pp,finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Twelve.Eightteen
```

```{r 12. PP Relationship SatisfactionMom X 17. Postpartum BondingDad}
Twelve.Seventeen <- cor.test(finaldt_4$MAT1pp,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Twelve.Seventeen 
```

```{r 13. PP Relationship SatisfactionDad X 14. PP ParentingMom}
Thirteen.Seventeen <- cor.test(finaldt_4$MAT2pp,finaldt_4$PARYCtot.1,use = "complete.obs", method = "pearson")
Thirteen.Seventeen 
```

```{r 13. PP Relationship SatisfactionDad X  15. PP ParentingDad}
Thirteen.Fifteen <- cor.test(finaldt_4$MAT2pp,finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Thirteen.Fifteen
```

```{r 13. PP Relationship SatisfactionDad X 16. Postpartum BondingMom}
Thirteen.Eightteen <- cor.test(finaldt_4$MAT2pp,finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Thirteen.Eightteen
```

```{r 13. PP Relationship SatisfactionDad X 17. Postpartum BondingDad}
Thirteen.Seventeen <- cor.test(finaldt_4$MAT2pp,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Thirteen.Seventeen 
```

```{r 14. PP ParentingMomX  15. PP ParentingDad}
Fourteen.Fifteen <- cor.test(finaldt_4$PARYCtot.1,finaldt_4$PARYCtot.2,use = "complete.obs", method = "pearson")
Fourteen.Fifteen
```

```{r 14. PP ParentingMomX 16. Postpartum BondingMom}
Fourteen.Sixteen <- cor.test(finaldt_4$PARYCtot.1,finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Fourteen.Sixteen
```

```{r 14. PP ParentingMomX 17. Postpartum BondingDad}
Fourteen.Seventeen <- cor.test(finaldt_4$PARYCtot.1,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Fourteen.Seventeen 
```

```{r 15. PP ParentingDad X 16. Postpartum BondingMom}
Fifteen.Sixteen <- cor.test(finaldt_4$PARYCtot.2,finaldt_4$PBQ.1,use = "complete.obs", method = "pearson")
Fifteen.Sixteen
```

```{r 15. PP ParentingDad X 17. Postpartum BondingDad}
Fifteen.Seventeen <- cor.test(finaldt_4$PARYCtot.2,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Fifteen.Seventeen 
```


```{r 16. Postpartum BondingMom X 17. Postpartum BondingDad}
Sixteen.Seventeen <- cor.test(finaldt_4$PBQ.1,finaldt_4$PBQ.2 ,use = "complete.obs", method = "pearson")
Sixteen.Seventeen 
```

# Supplementary Analyses

```{r Figure of correlation of fathers postpartum testosterone and postpartum MAT}
ggscatter(df_LONG, x = "MomTesto2", y = "MAT1pp", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Mothers' Postpartum Testosterone", ylab = "Mothers' Postpartum Marital Adjustment Test Score")
```

```{r Testosterone change and Postpartum Synchrony}
linearMod_CHANGE_2 <- lm(synchrony_2 ~ Dad_Change, data=finaldt_2)  # build linear regression model on full data
print(linearMod_CHANGE_2)
summary(linearMod_CHANGE_2)
```

```{r}
ggscatter(finaldt_2, x = "Dad_Change", y = "synchrony_2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Fathers' Testosterone Change from Prenatal to Postpartum", ylab = "Postpartum Synchrony")
```

```{r Correlate synchrony from prenatal to postpartums}
linearSynchrony <- lm(Postpartum_synchrony ~ Prenatal_synchrony)  # build linear regression model on full data
print(linearSynchrony)
summary(linearSynchrony)
```

```{r Figure Correlate synchrony from prenatal to postpartum}
ggscatter(finaldt_3, x = "synchrony", y = "synchrony_2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Postpartum Synchrony")
```

```{r Prenatal Synchrony and Prenatal Paternal Relationship}
linearPrenatalSynchrony_PaternalRelationship <- lm(pnDAStot.2 ~ synchrony, data=finaldt_3)  # build linear regression model on full data
print(linearPrenatalSynchrony_PaternalRelationship)
summary(linearPrenatalSynchrony_PaternalRelationship)
```

```{r}
ggscatter(finaldt_3, x = "synchrony", y = "DAStotpp.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Synchrony", ylab = "Paternal Pospartum Relationship Functioning")
```

```{r Prenatal and Postpartum Maternal Relationship}
linearMaternalRelationshipp <- lm(DAStotpp.1 ~ pnDAStot.1, data=finaldt_3)  # build linear regression model on full data
print(linearMaternalRelationshipp)
summary(linearMaternalRelationshipp)
```

```{r}
ggscatter(finaldt_3, x = "pnDAStot.1", y = "DAStotpp.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Maternal Relationship Functioning", ylab = "Postpartum Maternal Relationship Functioning")
```

```{r Prenatal and Postpartum Paternal Relationship}
linearPaternalRelationship <- lm(DAStotpp.2 ~ pnDAStot.2 , data=finaldt_3)  # build linear regression model on full data
print(linearPaternalRelationship)
summary(linearPaternalRelationship)
```

```{r}
ggscatter(finaldt_3, x = "pnDAStot.2", y = "DAStotpp.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Prenatal Paternal Relationship Functioning", ylab = "Postpartum Paternal Relationship Functioning")
```

```{r T-test Testosterone and Baby Age}
Corr_MomTesto1_x_bage3pp.1 <- t.test(df_LONG$MomTesto1 ~ df_LONG$Baby.sex, na.action = na.omit)
```

```{r}
Corr_MomTesto1_x_bage3pp.1
```

```{r}
Corr_DadTesto1_x_bage3pp.1 <- t.test(df_LONG$DadTesto1 ~ df_LONG$Baby.sex, na.action = na.omit)
```

```{r}
Corr_DadTesto1_x_bage3pp.1
```

```{r}
Corr_MomTesto2_x_bage3pp.1 <- t.test(df_LONG$MomTesto2 ~ df_LONG$Baby.sex, na.action = na.omit)
```

```{r}
Corr_MomTesto2_x_bage3pp.1
```


```{r}
Corr_DadTesto2_x_bage3pp.1 <- t.test(df_LONG$DadTesto2 ~ df_LONG$Baby.sex, na.action = na.omit)
```

```{r}
Corr_DadTesto2_x_bage3pp.1
```
```{r Making correlation of fathers prenatal testosterone and postpartum testosterone}
Corr_Pre_Dad_Testo_Sat <- cor.test(df_LONG$DadTesto1,df_LONG$pnDAStot.2,use = "complete.obs", method = "pearson")
Corr_Pre_Dad_Testo_Sat
```

```{r Making correlation of fathers prenatal testosterone and postpartum testosterone}
Corr_Pre_Dad_Testo_Sat <- cor.test(df_LONG$DadTesto1,df_LONG$pnDAStot.2,use = "complete.obs", method = "pearson")
Corr_Pre_Dad_Testo_Sat
```

```{r Making correlation of fathers prenatal testosterone and postpartum testosterone}
Corr_Pre_Dad_Testo_Sat <- cor.test(df_LONG$DadTesto1,df_LONG$pnDAStot.2,use = "complete.obs", method = "pearson")
Corr_Pre_Dad_Testo_Sat
```

```{r Final Results of correlation of fathers prenatal testosterone and postpartum testosterone}
Corr_Post_Dad_Testo_Sat <-cor.test(df_LONG$DadTesto2,df_LONG$DAStotpp.2,use = "complete.obs", method = "pearson")
```

```{r Figure of correlation of fathers prenatal testosterone and prenatal testosterone}
ggscatter(df_LONG, x = "DadTesto1", y = "pnDAStot.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Fathers Prenatal Testosterone", ylab = "Fathers' Prenatal Dyadic Adjustment Scale")
```

```{r Results of correlation of fathers postpartum testosterone and postpartum testosterone}

summary(Corr_Post_Dad_Testo_Sat)
```

```{r Figure of correlation of fathers postpartum testosterone and postpartum testosterone}
ggscatter(df_LONG, x = "DadTesto2", y = "DAStotpp.2", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Fathers Postpartum Testosterone", ylab = "Fathers' Postpartum Dyadic Adjustment Scale")
```

```{r Results of correlation of mothers prenatal testosterone and postpartum testosterone}

Corr_Pre_Mom_Testo_Sat <- cor.test(df_LONG$MomTesto1,df_LONG$pnDAStot.1,use = "complete.obs", method = "pearson")
Corr_Pre_Mom_Testo_Sat
summary(Corr_Pre_Mom_Testo_Sat)
```

```{r Figure of correlation of fathers postpartum testosterone and prenatal dyadic adjustment scale}
ggscatter(df_LONG, x = "MomTesto1", y = "pnDAStot.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Mothers' Prenatal Testosterone", ylab = "Mothers' Prenatal Dyadic Adjustment Scale")
```

```{r Results of correlation of mothers postpartum testosterone and postpartum dyadic adjustment scale}

Corr_Post_Mom_Testo_Sat <-cor.test(df_LONG$MomTesto2,df_LONG$DAStotpp.1,use = "complete.obs", method = "pearson")
Corr_Post_Mom_Testo_Sat
summary(Corr_Post_Mom_Testo_Sat)
```

```{r Figure of correlation of fathers postpartum testosterone and postpartum dyadic adjustment scale}
ggscatter(df_LONG, x = "MomTesto2", y = "DAStotpp.1", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Mothers' Postpartum Testosterone", ylab = "Mothers' Postpartum Dyadic Adjustment Scale")
```

```{r Results correlation of fathers postpartum testosterone and postpartum MAT}
Corr_Post_Dad_Testo_Adj <-cor.test(df_LONG$DadTesto2,df_LONG$MAT2pp, use = "complete", method = "pearson")
summary(Corr_Post_Dad_Testo_Adj)
```

```{r Figure correlation of fathers postpartum testosterone and postpartum MAT}
ggscatter(df_LONG, x = "DadTesto2", y = "MAT2pp", 
          add = "reg.line", conf.int = TRUE, 
          cor.coef = TRUE, cor.method = "pearson",
          xlab = "Fathers' Postpartum Testosterone", ylab = "Fathers' Postpartum Marital Adjustment Test Score")
```

```{r Results of correlation of fathers postpartum testosterone and postpartum MAT}
Corr_Post_Mom_Testo_Adj <-cor.test(df_LONG$MomTesto2,df_LONG$MAT1pp, use = "complete", method = "pearson")
Corr_Post_Mom_Testo_Adj
summary(Corr_Post_Mom_Testo_Adj)
```