---
title: "Synchrony_03.29.21_Continuous_Time"
output:
  html_document: default
  pdf_document: default
  toc: true
  toc_depth: 3  
---

## Preparation of R packages

```{r, setup=FALSE, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, Load packages, warning = FALSE, message=FALSE, echo=FALSE}

# Add additional packages you need
# To install a package, run the following ONCE (and only once on your computer)
# install.packages("psych")  
# install.packages ("ggpubr")
# install.packages("Publish")
# install.packages("ggubr")
# install.packages("corrplot")
# install.packages("RColorBrewer")
# install.packages("ggpubr")
# install.packages("lme4")
# install.packages("lmerTest")
# install.packages("multilevelTools")
# install.packages("pastecs")
# install.packages("qwraps2")
# install.packages(apaTables)
# install.packages(apa.d.table)
# install.packages(apa.descriptive)
# install.packages(apa.cor.table)
# install.packages(Gmisc)
# install.packages('ltm')
# install.packages("Hmisc")
# install.packages("reshape2")

library(ltm)
library(qwraps2)
library(multilevelTools)
library(lme4)
library(lmerTest)
library(ggpubr)
library(Publish) 
library(here)  # makes reading data more consistent
library(haven)  # for importing SPSS/SAS/Stata data
library(brms)  # for Bayesian multilevel analysis
library(lattice)  # for dotplot (working with lme4)
library(sjPlot)  # for plotting effects
library(broom.mixed)  # for summarizing results
library(interactions)  # for plotting interactions
library(modelsummary)  # for making tables
library(psych)
library(ggpubr)
library(lmerTest)
library(corrplot)
library(RColorBrewer)
library(ggpubr)
library(pastecs)
library(apaTables)
library(tidyr)
library(dplyr)
library(tidyverse)  # for data manipulation and plotting
library(haven)  # for importing SPSS/SAS/Stata data
library(brms)  # for Bayesian multilevel analysis
library(lattice)  # for dotplot (working with lme4)
library(interactions)  # for plotting interaction
library(rstan)
library(foreign)
library(foreign)
library(reshape2)

# Add the following so that the LOO will be included in the msummary table
msummary_mixed <- function(models, coef_map = NULL, add_rows = NULL, ...) {
  if (is.null(coef_map)) {
    if (!"list" %in% class(models)) {
      models <- list(models)
    }
    for (model in models) {
      coef_map <- union(coef_map, tidy(model)$term)
    }
  }
  ranef_index <- grep("^(sd|cor)__", x = coef_map)
  coef_map <- c(coef_map[-ranef_index], coef_map[ranef_index])
  names(coef_map) <- coef_map
library(dplyr)
  rows <- data.frame(term = c("Fixed Effects", "Random Effects"))
  rows <- cbind(rows, rbind(rep("", length(models)), 
                            rep("", length(models))))
  length_fes <- length(coef_map) - length(ranef_index)
  attr(rows, 'position') <- c(1, (length_fes + 1) * 2)
  modelsummary::msummary(models, coef_map = coef_map, add_rows = rows, ...)
}
theme_set(theme_bw())  # Theme; just my personal preference
```

## When working with new SPSS folder, rename Test Variables in SPSS

1. Current OG file: HATCH 7.31.2020

2. Current renamed file: HATCH_07.31.20_08.08.21

3. Rename testosterone variables in SPSS...
Testo1pn.1.trunc--->Mom11
Testo3pn.1.trunc--->Mom21
Testo6pn.1.trunc--->Mom31
Testo1pp.1trunc--->Mom42
Testo3pp.1trunc--->Mom52
Testo6pp.1trunc--->Mom62
Testo1pn.2.trunc--->Dad11
Testo3pn.2.trunc--->Dad21
Testo6pn.2.trunc--->Dad31
Testo1pp.2.00--->Dad42
Testo3pp.2.00--->Dad52
Testo6pp.2.00--->Dad62

4. Make new variable by calculate average scores in SPSS...
(The syntax is HATCH_07.31.20_08.08.21)
MomTesto1 (which is the average of mom prenatal testosterone)
MomTesto2 (which is the average of mom postpartum testosterone)
DadTesto1 (which is the average of dad prenatal testosterone)
DadTesto2 (which is the average of dad postpartum testosterone)
DadAge (which is the average of dad age)

5.Organize these variables to the front...
CoupID
RelStat
bage6pp
GestationalAgeWeeks
pnAge_1.1
pnAge_1.2
Age_1.1
Age_1.2
DadAge
Ethnicity.1
Ethnicity.2
Education.1
Education.2
Mom111
Mom221
Mom331
Mom412
Mom522
Mom632
Dad111
Dad221
Dad331
Dad412
Dad522
Dad632
MomTesto1
MomTesto2
DadTesto1
DadTesto2
PARYCse.1
PARYCse.2
PARYCpa.1
PARYCpa.2
PARYCtot.1
PARYCtot.2
DAStotpp.1
DAStotpp.2
pnMaritalSat.1
pnMaritalSat.2
MAT1pp
MAT2pp
PBQ.1
PBQ.2

# Data preparation

```{r , warning = FALSE, message=FALSE, message=FALSE}
df_WIDE <- read.spss('/Users/sofiacardenas/Desktop/April_30_MLM/Final_Project/4.Analyses/HATCH_07.31.20_08.08.21.sav')
```

```{r, warning = FALSE, message=FALSE, message=FALSE}
df_WIDE$Baby.sex <- factor(df_WIDE$Baby.sex)
```

```{r, warning = FALSE, message=FALSE, message=FALSE}
df_WIDE <- data.frame(df_WIDE)
```

# Convert factor continuous wkday and wkend hours 

```{r, warning = FALSE, message=FALSE, echo=FALSE}
df_WIDE$weeksbfdue.2 <- as.numeric(df_WIDE$weeksbfdue.2)
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
df_WIDE$bage6pp <- as.numeric(df_WIDE$bage6pp)
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
df_WIDE <- read.spss('/Users/sofiacardenas/Desktop/April_30_MLM/Final_Project/4.Analyses/HATCH_07.31.20_08.08.21.sav')
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
df_WIDE$Baby.sex <- factor(df_WIDE$Baby.sex)
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
df_WIDE <- data.frame(df_WIDE)
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
# Using the new `tidyr::pivot_longer()` function
df_LONG <- df_WIDE %>% 
  pivot_longer(
    c(Mom111:Dad632), # variables that are repeated measures
    # Convert 8 columns to 3: 2 columns each for anti/read (.value), and 
    # one column for time
    names_to = c(".value", "Testo_Measurement", "Sample", "Time"),
    # Extract the names "anti"/"read" from the names of the variables for the 
    # value columns, and then the number to the "time" column
    names_pattern = "(Mom|Dad)([1-6])([1-3])([1-2])", 
    # Convert the "time" column to integers
    names_transform = list(time = as.integer)
    )
``` 

```{r, warning = FALSE, message=FALSE, echo=FALSE}
df_LONG %>% 
  select(CoupID, Testo_Measurement, weeksbfdue.2, bage6pp, Mom, Dad, everything())
```

# Unconditional model for dad testosterone

```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
m0_Model_daddy <- brm(Dad ~ (1 | CoupID), 
                      seed = 2152, control = list(max_treedepth = 15), chains = 8,iter = 4000, data = df_LONG)

echo=FALSE

```

# Print unconditional model for dad testosterone 

# Using dad unconditional model to assess prenatal intra-class correlation and decompose variance

```{r, warning = FALSE, message=FALSE, echo=FALSE}
# Warning: Rows containing NAs were excluded from the model.
testo_daddy <- posterior_samples(m0_Model_daddy, pars = c("sd", "sigma"))

# Posterior of ICC: tau_0^2 / (tau_0^2 + sigma^2)
icc_samples_daddy <- testo_daddy$sd_CoupID__Intercept^2 / 
  (testo_daddy$sd_CoupID__Intercept^2 + testo_daddy$sigma^2)

# Print ICCs
c(daddy = mean(icc_samples_daddy))
```

# Unconditional model for mom testosterone 
```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
m0_Model_mommy <- brm(Mom ~ (1 | CoupID), 
                      seed = 2154, control = list(max_treedepth = 15), chains = 8,iter = 4000, data = df_LONG)

```

# Print unconditional model for mom testosterone 
```{r, warning = FALSE, message=FALSE, echo=FALSE}
m0_Model_mommy
```

# Using mom unconditional model to assess prenatal intra-class correlation and decompose variance

```{r, warning = FALSE, message=FALSE, echo=FALSE}
# Warning: Rows containing NAs were excluded from the model.
# Daddy (expectant dad-testosterone)
testo_mommy <- posterior_samples(m0_Model_mommy, pars = c("sd", "sigma"))

# Posterior of ICC: tau_0^2 / (tau_0^2 + sigma^2)
icc_samples_mommy <- testo_mommy$sd_CoupID__Intercept^2 / 
  (testo_mommy$sd_CoupID__Intercept^2 + testo_mommy$sigma^2)

# Print ICCs
c(mommy = mean(icc_samples_mommy))
```

# Cluster-mean centering of mom testosterone, fit a model that decomposes the association between dad and mom testosteone into the person-level and the couple-level effects.
```{r, warning = FALSE, message=FALSE, message=FALSE, echo=FALSE}
df_LONG <- df_LONG %>% 
  group_by(CoupID) %>%   # operate within countrr
  mutate(Mom_cm = mean(Mom),   # create cluster means (the same as  `meanses`)
         Mom_cmc = Mom - Mom_cm) %>%   # cluster-mean centered
  ungroup()  # exit the "editing within groups" mode
```

### Hypothesis 1 

```{r, Prenatal MLM model, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony <- brm(Dad ~ weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

### Hypothesis 1 Model 

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
augment(Bayesian_Synchrony) %>% 
  mutate(Mom = Mom_cmc + Mom_cm) %>% 
  ggplot(aes(x = Mom, y = Dad, color = factor(CoupID))) +
  # Add points
  geom_point(size = 0.5, alpha = 0.2) + 
  # Add within-cluster lines
  geom_smooth(aes(y = .fitted), 
              method = "lm", se = FALSE, size = 0.5) + 
  # Add group means
  stat_summary(aes(x = Mom, y = .fitted, 
                   fill = factor(CoupID)), 
               color = "red",  # add border
               fun = mean, 
               geom = "point",
               shape = 24,
               # use triangles
               size = 2.5) + 
  # Add between coefficient
  geom_smooth(aes(x = Mom, y = .fitted), 
              method = "lm", se = TRUE, 
              color = "black") + 
  labs(y = "Dad") + 
  # Suppress legend
  guides(color = FALSE, fill = FALSE)
```

# Hypothesis 3 Synchrony X Postpartum Marital Satistifaction 

```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony_Post_MarSat <- brm(Dad ~ MAT2pp + weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + MAT2pp*weeksbfdue.2 + MAT2pp*bage6pp + MAT2pp*Mom_cm +  MAT2pp*Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

# Hypothesis 3 Model Synchrony X Postpartum Marital Satistifaction

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony_Post_MarSat
```

# Convert factor continuous wkday and wkend hours 

```{r,}
df_LONG$wkdayhourswithbaby.1.6pp <- as.numeric(df_LONG$wkdayhourswithbaby.1.6pp)
```

```{r,}
df_LONG$wkdayhourswithbaby.2.6pp <- as.numeric(df_LONG$wkdayhourswithbaby.2.6pp)
```

```{r,}
df_LONG$wkendhourswithbaby.1.6pp <- as.numeric(df_LONG$wkendhourswithbaby.1.6pp)
```

```{r,}
df_LONG$wkendhourswithbaby.2.6pp <- as.numeric(df_LONG$wkendhourswithbaby.2.6pp)
```

```{r,}
df_LONG$wkdayalonewithbaby.1.6pp <- as.numeric(df_LONG$wkdayalonewithbaby.1.6pp)
```

```{r,}
df_LONG$wkdayalonewithbaby.2.6pp <- as.numeric(df_LONG$wkdayalonewithbaby.2.6pp)
```

```{r,}
df_LONG$wkendalonewithbaby.1.6pp <- as.numeric(df_LONG$wkendalonewithbaby.1.6pp)
```

```{r,}
df_LONG$wkendhalonewithbaby.2.6pp <- as.numeric(df_LONG$wkendhalonewithbaby.2.6pp)
```

# Hypothesis 3 Equation Synchrony X Week time 

```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony_weekhours <- brm(Dad ~ wkdayhourswithbaby.2.6pp + weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + wkdayhourswithbaby.2.6pp*weeksbfdue.2 + wkdayhourswithbaby.2.6pp*bage6pp + wkdayhourswithbaby.2.6pp*Mom_cm + wkdayhourswithbaby.2.6pp*Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

# Hypothesis 3 Model Synchrony X Week time

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony_weekhours
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
interact_plot(Bayesian_Synchrony_weekhours, 
              pred = "Mom_cmc",
              modx = "bage6pp",
              modx.labels = "Weeks postpartum",
              plot.points = TRUE, 
              point.size = 0.5, 
              point.alpha = 0.2, 
              facet.modx = TRUE,  # use this to make two panels
              x.label = "Mothers' Cluster Mean Centered Testosterone", 
              y.label = "Fathers' Testosterone")
```

# Hypothesis 3 Equation Synchrony X Week time alone

```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony_weekhoursalone <- brm(Dad ~ wkdayalonewithbaby.2.6pp + weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + wkdayalonewithbaby.2.6pp*weeksbfdue.2 + wkdayhourswithbaby.2.6pp*bage6pp + wkdayalonewithbaby.2.6pp*Mom_cm + wkdayalonewithbaby.2.6pp*Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)
```

# Hypothesis 3 Model Synchrony X Week time alone

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony_weekhoursalone
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
interact_plot(Bayesian_Synchrony_weekhoursalone, 
              pred = "Mom_cm",
              modx = "wkdayalonewithbaby.2.6pp",
              modx.labels = "Fathers' Weekday Hours Alone with Baby",
              plot.points = TRUE, 
              point.size = 0.5, 
              point.alpha = 0.2, 
              facet.modx = TRUE, 
              x.label = "Mothers' mean cluster centered testosterone", 
              y.label = "Fathers' Testosterone")
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
interact_plot(Bayesian_Synchrony_weekhoursalone, 
              pred = "weeksbfdue.2",
              modx = "wkdayalonewithbaby.2.6pp",
              modx.labels = "Fathers' Week Days Alone with Baby",
              plot.points = TRUE, 
              point.size = 0.5, 
              point.alpha = 0.2, 
              facet.modx = TRUE, 
              x.label = "Weeks Before Infant Due", 
              y.label = "Fathers' Testosterone")
```

# Hypothesis 3 Equation Synchrony X Weekend time

```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony_weekendhours <- brm(Dad ~ wkendhourswithbaby.2.6pp + weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + wkendhourswithbaby.2.6pp*weeksbfdue.2 + wkendhourswithbaby.2.6pp*bage6pp + wkendhourswithbaby.2.6pp*Mom_cm + wkendhourswithbaby.1.6pp*Mom_cmc + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

# Hypothesis 3 Model Synchrony X Weekend time

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony_weekendhours
```

# Hypothesis 3 Equation Synchrony X Weekend time alone

```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony_weekendhoursalone <- brm(Dad ~ wkendhalonewithbaby.2.6pp + weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + wkendhalonewithbaby.2.6pp*weeksbfdue.2 + wkendhalonewithbaby.2.6pp*bage6pp + wkendhalonewithbaby.2.6pp*Mom_cm + wkendhalonewithbaby.2.6pp*Mom_cmc + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

# Hypothesis 3 Model Synchrony X Weekend time alone

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony_weekendhours
```

# Hypothesis 3 Synchrony X Prenatal Marital Satistifaction Mom

```{r,, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony_WO_Cross_MarSat_Mom_Pre <- brm(Dad ~ pnMaritalSat.1 + MAT1pp + weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + pnMaritalSat.1*bage6pp + pnMaritalSat.1*weeksbfdue.2 + pnMaritalSat.1*Mom_cm +  pnMaritalSat.1*Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

# Hypothesis 3 Model Synchrony X Prenatal Marital Satistifaction Mom

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony_WO_Cross_MarSat_Mom_Pre
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
interact_plot(Bayesian_Synchrony_WO_Cross_MarSat_Mom_Pre, 
              pred = "pnMaritalSat.1",
              modx = "weeksbfdue.2",
              modx.labels = "Weeks Before Infant Due",
              plot.points = TRUE, 
              point.size = 0.5, 
              point.alpha = 0.2, 
              facet.modx = TRUE,  # use this to make two panels
              x.label = "Mothers prenatal Marital Satisfaction", 
              y.label = "Fathers' Testosterone")
```

# Hypothesis 3 Equation Synchrony X Week time Mom 

```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony_weekhours_Mom <- brm(Dad ~ wkdayhourswithbaby.1.6pp + weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + wkdayhourswithbaby.1.6pp*weeksbfdue.2 + wkdayhourswithbaby.1.6pp*bage6pp + wkdayhourswithbaby.1.6pp*Mom_cm + wkdayhourswithbaby.1.6pp*Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

# Hypothesis 3 Model Synchrony X Week time Mom 

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony_weekhours_Mom
```

# Hypothesis 3 Equation Synchrony X Week time Mom alone

```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony_weekhours_Momalone <- brm(Dad ~ wkdayalonewithbaby.1.6pp + weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + wkdayalonewithbaby.1.6pp*weeksbfdue.2 + wkdayalonewithbaby.1.6pp*bage6pp + wkdayalonewithbaby.1.6pp*Mom_cm + wkdayalonewithbaby.1.6pp*Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

# Hypothesis 3 Model Synchrony X Week time Mom alone 

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony_weekhours_Mom
```

# Hypothesis 3 Equation Synchrony X Weekend time Mom

```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony_weekendhours_Mom <- brm(Dad ~ wkendhourswithbaby.1.6pp + weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + wkendhourswithbaby.1.6pp*weeksbfdue.2 + wkendhourswithbaby.1.6pp*bage6pp + wkendhourswithbaby.1.6pp*Mom_cm + wkendhourswithbaby.1.6pp*Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

# Hypothesis 3 Model Synchrony X Weekend time Mom

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony_weekendhours_Mom
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
interact_plot(Bayesian_Synchrony_weekendhours_Mom, 
              pred = "Mom_cm",
              modx = "wkendhourswithbaby.1.6pp",
              modx.labels = "Mom Weekend Hours with Baby",
              plot.points = TRUE, 
              point.size = 0.5, 
              point.alpha = 0.2, 
              facet.modx = TRUE,  # use this to make two panels
              x.label = "Mom Cluster Centered Testosterone", 
              y.label = "Fathers' Testosterone")
```

# Hypothesis 3 Equation Synchrony X Weekend time Mom alone

```{r, warning = FALSE, message=FALSE, echo=FALSE, results='hide'}
Bayesian_Synchrony_weekendhours_Momalone <- brm(Dad ~ wkendalonewithbaby.1.6pp + weeksbfdue.2 + bage6pp + Mom_cm + Mom_cmc + wkendalonewithbaby.1.6pp*weeksbfdue.2 + wkendalonewithbaby.1.6pp*bage6pp + wkendalonewithbaby.1.6pp*Mom_cm + wkendalonewithbaby.1.6pp*Mom_cmc + Mom_cmc*weeksbfdue.2 + Mom_cmc*bage6pp + (Mom_cmc | CoupID),
               seed = 2155,
               control = list(max_treedepth = 15, adapt_delta = .995),
               chains = 8, 
               iter = 4000, data = df_LONG)

```

# Hypothesis 3 Model Synchrony X Weekend time Mom alone 

```{r, warning = FALSE, message=FALSE, echo=FALSE}
Bayesian_Synchrony_weekendhours_Momalone
```

```{r, warning = FALSE, message=FALSE, echo=FALSE}
interact_plot(Bayesian_Synchrony_weekendhours_Momalone, 
              pred = "Mom_cm",
              modx = "bage6pp",
              modx.labels = "Baby age",
              plot.points = TRUE, 
              point.size = 0.5, 
              point.alpha = 0.2, 
              facet.modx = TRUE,  # use this to make two panels
              x.label = "Mom Cluster Centered Testosterone", 
              y.label = "Fathers' Testosterone")
```